\documentclass{article}

\usepackage{mathrsfs,amsmath}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{minted}
\usepackage{mwe}

\usepackage[margin=1.4in]{geometry}

\title{Assignment \#4 | CS 362 Software Engineering}
\author{Jared Dyreson \\
        jareddyreson@csu.fullerton.edu \\
        California State University, Fullerton}
\date

\DeclareRobustCommand{\bowtie}{%
  \mathrel\triangleright\joinrel\mathrel\triangleleft}


\usepackage [english]{babel}
\usepackage [autostyle, english = american]{csquotes}
\MakeOuterQuote{"}

\titlespacing*{\section}
{0pt}{5.5ex plus 1ex minus .2ex}{4.3ex plus .2ex}
\titlespacing*{\subsection}
{0pt}{5.5ex plus 1ex minus .2ex}{4.3ex plus .2ex}

\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}

\begin{document}

\maketitle
\tableofcontents

\newpage

\section{Chapter 13 | Design Concepts and Principles}

During the design process, it is important for engineers to come up with multiple solutions for the problem at hand, picking the best one.
This leads to a more wholistic approach and allows for a more robust implementation.
Open discussions with others can also highlight strengths and weaknesses in each other's ideas.


After that, all components should get stitched together, in a modular fashion.
This will allow for refinement and improvement on each component, without disrupting the others.
\emph{Functional independence} is a direct byproduct of modularity, allowing it to not be strictly dependent of.
This leads to fast production and problems can easily be traced.
Cohesion is the act of linking two modules together, and it itself is independent of the two modules.

However, when software is too intermingled through the process of \emph{coupling}, distinct errors occur.
The codebase becomes monolithic, inefficient and hard to maintain over time.
Limiting such actions is strongly encouraged, and links should only be made at crucial moments.
Take a compiler for example (I had to write on this semester, yay!); it is comprised of a lexer, parser and code generator.
It would be foolish for the lexer to be deeply embedded into the parser.
All the lexer is concerned with is token generation and the parser is processing said tokens.
Any changes to the lexer would result to changes made to the parser, if coupled deeply.

Strong designs are crucial for software quality assessments.
Design construction leads to better code written, because the requirements and boundaries are clearly defined.
Everyone on the team knows what to do and will use the proper tools to complete the task.
Tasks can be efficiently delegate amongst individuals via a ticket system.


\end{document}
